|

### 2020-12-01 manuscript/article.Rmd
commit 11/30

```

@@

We see similar results when we compare $n$ with log expenditure per capita. In
this model, the average effect size is `r round(mod[[3]]$TE.random,3)` and the standard error is
`r round(mod[[3]]$seTE.random,3)` (studies = `r mod[[3]]$k`, 95\% CI = [`r round(mod[[3]]$lower.random,3)`; `r round(mod[[3]]$upper.random,3)`], $p$-value = `r round(mod[[3]]$pval.random,3)`, prediction
interval = [-0.618; 0.481]; $I^2$ = 92.5\%). The coefficient is 
statistically indistinguishable from zero.

In our restricted sample, larger lower house size also does not increase
government spending as a percentage of GDP (studies = `r mod[[5]]$k`, SMD = `r round(mod[[5]]$TE.random,3)`, SE =
`r round(mod[[5]]$seTE.random,3)`, 95\% CI = [`r round(mod[[5]]$lower.random,3)`; `r round(mod[[5]]$upper.random,3)`], $p$-value = `r round(mod[[5]]$pval.random,3)`, prediction interval =
[-0.105; 0.089], $I^2$ = 87.1\%). We find a positive effect in our extended
sample and the coefficient is statistically significant at the 10\% level
(coefficients = 21, SMD = 0.008, SE = 0.004, 95\% CI = [-0.000; 0.016], $p$-value =
0.058, prediction interval = [-0.026; 0.042], $I^2$ = 98.5\%). The 
result supports the "law of 1/$n$", but the evidence is moderate
as the prediction interval include zero.

@@

Next, we present the meta-analyses using log($n$), the logarithm of lower house
size, as the main explanatory variable. We start with the relationship between
log($n$) and the logarithm of expenditure per capita. The result is positive and
statistically significant at 10\%, but the prediction interval encompasses zero
(studies = `r mod[[4]]$k`, SMD = `r round(mod[[4]]$TE.random,3)`, SE = `r round(mod[[4]]$seTE.random,3)`, 95\% CI = [`r round(mod[[4]]$lower.random,3)`; `r round(mod[[4]]$upper.random,3)`], $p$-value =
`r round(mod[[4]]$pval.random,3)`, prediction interval = [-1.258; 1.627], $I^2$ = 85.9\%). Although the
coefficient has the predicted sign, we should interpret the finding with caution
as it does not replicate in our sample of 126 effect sizes.

Our model that correlates log($n$) with public expenditures as a percentage of
GDP fails to reach conventional levels of statistical significance (studies =
`r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = `r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`; `r round(mod[[6]]$upper.random,3)`], $p$-value = `r round(mod[[6]]$pval.random,3)`,
prediction interval = [-36.206; 36.246], $I^2$ = 96.1\%). The extended sample
also gives us a null result.

The third set of models uses $k$, upper house size, as the main independent
variable. We find a positive correlation between $k$ and expenditure per capita
and the coefficient is significant at a 10\% level (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
= `r round(mod[[2]]$seTE.random,3)`, 95\% CI = [`r round(mod[[2]]$lower.random,3)`; `r round(mod[[2]]$upper.random,3)`], $p$-value = `r round(mod[[2]]$pval.random,3)`, prediction interval =
[-21.130; 42.357], $I^2$ = 79.4\%). But as with the other models, the prediction
interval again includes zero. When we run the same analysis in the extended
sample, we also see a significant coefficient yet a prediction interval that
contains zero (coefficients = 24, SMD = 7.216, SE = 1.342, 95\% CI = [4.440; 9.992],
$p$-value $<$ 0.0001, prediction interval = [-1.222; 15.654], $I^2$ = 77.7\%).

Our last estimation analyses the relationship between $k$ and government
spending as a percentage of GDP. The coefficient is not statistically
significant, indicating a null effect (studies = `r mod[[7]]$k`, SMD = `r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI
= [`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`], $p$-value = `r round(mod[[7]]$pval.random,3)`, prediction interval = [-0.428; 0.423],
$I^2$ = 85.8\%). The result is very similar in the extended sample.

>>>>

# Full model - Pooling effects analysis -- PCTGDP x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod[[8]] <- metagen(coef, SE, data = aux,
          studlab = paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm = "SMD")

# Full data - Pooling effects analysis -- ExpPC x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod[[9]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
```

@@

We see similar results when we compare $n$ with log expenditure per capita. In
this model, the average effect size is `r round(mod[[3]]$TE.random,3)` and the standard error is
`r round(mod[[3]]$seTE.random,3)` (studies = `r mod[[3]]$k`, 95\% CI = [`r round(mod[[3]]$lower.random,3)`; `r round(mod[[3]]$upper.random,3)`], $p$-value = `r round(mod[[3]]$pval.random,3)`, prediction
interval = [`r round(mod[[3]]$lower.predict,3)`; `r round(mod[[3]]$upper.predict,3)`]; $I^2$ = `r round(mod[[3]]$I2*100, 2)`\%). The coefficient is 
statistically indistinguishable from zero.

In our restricted sample, larger lower house size also does not increase
government spending as a percentage of GDP (studies = `r mod[[5]]$k`, SMD = `r round(mod[[5]]$TE.random,3)`, SE =
`r round(mod[[5]]$seTE.random,3)`, 95\% CI = [`r round(mod[[5]]$lower.random,3)`; `r round(mod[[5]]$upper.random,3)`], $p$-value = `r round(mod[[5]]$pval.random,3)`, prediction interval =
[`r round(mod[[5]]$lower.predict,3)`; `r round(mod[[5]]$upper.predict,3)`], $I^2$ = `r round(mod[[5]]$I2*100, 2)`\%). We find a positive effect in our extended
sample and the coefficient is statistically significant at the 10\% level
(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; `r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
result supports the "law of 1/$n$", but the evidence is moderate
as the prediction interval include zero.

@@

Next, we present the meta-analyses using log($n$), the logarithm of lower house
size, as the main explanatory variable. We start with the relationship between
log($n$) and the logarithm of expenditure per capita. The result is positive and
statistically significant at 10\%, but the prediction interval encompasses zero
(studies = `r mod[[4]]$k`, SMD = `r round(mod[[4]]$TE.random,3)`, SE = `r round(mod[[4]]$seTE.random,3)`, 95\% CI = [`r round(mod[[4]]$lower.random,3)`; `r round(mod[[4]]$upper.random,3)`], $p$-value =
`r round(mod[[4]]$pval.random,3)`, prediction interval = [`r round(mod[[4]]$lower.predict,3)`; `r round(mod[[4]]$upper.predict,3)`], $I^2$ = `r round(mod[[4]]$I2*100, 2)`\%). Although the
coefficient has the predicted sign, we should interpret the finding with caution
as it does not replicate in our sample of `r dim(fulldat)[1]` effect sizes.

Our model that correlates log($n$) with public expenditures as a percentage of
GDP fails to reach conventional levels of statistical significance (studies =
`r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = `r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`; `r round(mod[[6]]$upper.random,3)`], $p$-value = `r round(mod[[6]]$pval.random,3)`,
prediction interval = [`r round(mod[[6]]$lower.predict,3)`; `r round(mod[[6]]$upper.predict,3)`], $I^2$ = `r round(mod[[6]]$I2*100, 2)`\%). The extended sample
also gives us a null result.

The third set of models uses $k$, upper house size, as the main independent
variable. We find a positive correlation between $k$ and expenditure per capita
and the coefficient is significant at a 10\% level (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
= `r round(mod[[2]]$seTE.random,3)`, 95\% CI = [`r round(mod[[2]]$lower.random,3)`; `r round(mod[[2]]$upper.random,3)`], $p$-value = `r round(mod[[2]]$pval.random,3)`, prediction interval =
[`r round(mod[[2]]$lower.predict,3)`; `r round(mod[[2]]$upper.predict,3)`], $I^2$ = `r round(mod[[2]]$I2*100, 2)`\%). But as with the other models, the prediction
interval again includes zero. When we run the same analysis in the extended
sample, we also see a significant coefficient yet a prediction interval that
contains zero (coefficients = `r mod[[9]]$k`, SMD = `r round(mod[[9]]$TE.random,3)`, SE = `r round(mod[[9]]$seTE.random,3)`, 95\% CI = [`r round(mod[[9]]$lower.random,3)`; `r round(mod[[9]]$upper.random,3)`],
$p$-value $<$ 0.001, prediction interval = [`r round(mod[[9]]$lower.predict,3)`; `r round(mod[[9]]$upper.predict,3)`], $I^2$ = `r round(mod[[9]]$I2*100, 2)`\%).

Our last estimation analyses the relationship between $k$ and government
spending as a percentage of GDP. The coefficient is not statistically
significant, indicating a null effect (studies = `r mod[[7]]$k`, SMD = `r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI
= [`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`], $p$-value = `r round(mod[[7]]$pval.random,3)`, prediction interval = [`r round(mod[[7]]$lower.predict,3)`; `r round(mod[[7]]$upper.predict,3)`],
$I^2$ = `r round(mod[[7]]$I2*100, 2)`\%). The result is very similar in the extended sample.
